A National Pipeline System as a Solution to Future Water Shortage in the United States

### 2013-02-05 paper.tex
Fix some references

\begin{figure}[h]
        \centering
        \includegraphics[width=\textwidth]{25minus05}
        \caption{Visualization of projected increase in water usage, by county. Red is high, green is low or negative (i.e. projected decrease).}
        \label{fig:outline}
\end{figure}

@@

\begin{table}[h]
\label{table:priority}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
FIPS1 & FIPS 2 & Priority \tabularnewline
\hline
48201 & 48339 & 10346.3 \tabularnewline
\hline
24005 & 24510 & 10675.4 \tabularnewline
\hline
6001  &6013 & 11019.8 \tabularnewline
\hline
34003 & 34017 & 11190.7 \tabularnewline
\hline
51153 & 51685 & 12104.5 \tabularnewline
\hline
11001 & 51013 & 12113.6 \tabularnewline
\hline
48029 & 48091 & 13787.1 \tabularnewline
\hline
34017 & 36061 & 16584.3 \tabularnewline
\hline
51059 & 51600 & 18528.8 \tabularnewline
\hline
51153 & 51683 & 22134.2 \tabularnewline
\hline
6037 & 6059  &23742.4 \tabularnewline
\hline
36047 & 36061  &27446.1 \tabularnewline
\hline
36059 & 36081  &29256.5 \tabularnewline
\hline
36005 & 36061 & 32595 \tabularnewline
\hline
36047 & 36081 & 33517.6 \tabularnewline
\hline
17031 & 17043 & 41637.4 \tabularnewline
\hline

\end{tabular}
\caption{Last 17 (highest priority) rows of the table of priority ranks of pipelines to be built.}
\end{center}
\end{table}

@@

\subsubsection{Data Origin}
As the problem of water distribution and availability is very much determined by the geographic location and conditions, we obtained a dataset containing the outlines and geographic locations of every county in the United States, which we then used in our county level analysis. Figure \ref{fig:outline} shows a visualization of the contents of this data set. For the method of visualization used, see Section \ref{sec:vis}.

\subsubsection{Data Processing}
The dataset we obtained was in the proprietary, binary "Shapefile" format, that is used by many professional GIS systems. Luckily, there exists an open documentation of the format \cite{shapefile-gis}, which allowed us to implement our own parser to extract the locations, and shapes of the various counties.

>>>>

\begin{figure}[h]
        \centering
        \includegraphics[width=\textwidth]{25minus05}
        \caption{Visualization of projected increase in water usage, by county. Red is high, green is low, and cyan is projected decrease.}
        \label{fig:25minus05}
\end{figure}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
FIPS1 & FIPS 2 & Priority \tabularnewline
\hline
48201 & 48339 & 10346.3 \tabularnewline
\hline
24005 & 24510 & 10675.4 \tabularnewline
\hline
6001  &6013 & 11019.8 \tabularnewline
\hline
34003 & 34017 & 11190.7 \tabularnewline
\hline
51153 & 51685 & 12104.5 \tabularnewline
\hline
11001 & 51013 & 12113.6 \tabularnewline
\hline
48029 & 48091 & 13787.1 \tabularnewline
\hline
34017 & 36061 & 16584.3 \tabularnewline
\hline
51059 & 51600 & 18528.8 \tabularnewline
\hline
51153 & 51683 & 22134.2 \tabularnewline
\hline
6037 & 6059  &23742.4 \tabularnewline
\hline
36047 & 36061  &27446.1 \tabularnewline
\hline
36059 & 36081  &29256.5 \tabularnewline
\hline
36005 & 36061 & 32595 \tabularnewline
\hline
36047 & 36081 & 33517.6 \tabularnewline
\hline
17031 & 17043 & 41637.4 \tabularnewline
\hline

\end{tabular}
\caption{Last 17 (highest priority) rows of the table of priority ranks of pipelines to be built.}
\label{table:priority}
\end{center}
\end{table}

@@

\subsubsection{Data Origin}
As the problem of water distribution and availability is very much determined by the geographic location and conditions, we obtained a dataset containing the outlines and geographic locations of every county in the United States \cite{arcgis}, which we then used in our county level analysis. Figure \ref{fig:outline} shows a visualization of the contents of this data set. For the method of visualization used, see Section \ref{sec:vis}.

\subsubsection{Data Processing}
The dataset we obtained was in the proprietary, binary "Shapefile" format, that is used by many professional GIS systems. Luckily, there exists an open documentation of the format \cite{shapefile-spec}, which allowed us to implement our own parser to extract the locations, and shapes of the various counties.
